WSClean: an implementation of a fast, generic wide-field imager for radio astronomy

### 2014-03-31 articles/2014/Article-WSClean/wsclean.tex

In practice, the final scaling will be different from $\left(w_{\max} - w_{\min}\right)/\sqrt{1-l^2-m^2}$ suggested by Eq.~\eqref{eq:wstacking}, because the individual $w$-layers will not be completely filled with samples. Therefore, the number of added samples and their weights have to be taken into account. Therefore, each pixel is divided by the weighted number of samples. Additionally, it might be required to divide out the effect of a possible convolution kernel, the primary beam and correct for other direction-dependent effects. In XX, YY, LL or RR polarisations, a correlated baseline is the complex conjugate of the reversed baseline, and the relation $V(u,v,w)=\overline{V(-u,-v,-w)}$ holds. The right-hand side of Eq.\eqref{eq:wstacking} with only positive $w$-value samples then becomes the complex conjugate of the one with only negative $w$-value samples. In this case we can therefore calculate the image for $w<0$ from the image with $w>0$. That allows us to set $w_{\min}$ to the minimum absolute $w$-value, which requires half the number of layers. In any case, the input to the two-dimensional inverse FFT is not generally a Hermitian-symmetric function, and hence the inverse FFT is always performed as a complex-to-complex transform.

>>>>

In practice, the final scaling will be different from $\left(w_{\max} - w_{\min}\right)/\sqrt{1-l^2-m^2}$ suggested by Eq.~\eqref{eq:wstacking}, because the individual $w$-layers will not be completely filled with samples. Therefore, each pixel is divided by the weighted number of samples. Additionally, it might be required to divide out the effect of a possible convolution kernel, the primary beam and correct for other direction-dependent effects. In equally-polarized baselines (e.g., XX, YY, LL or RR), a correlated baseline is the complex conjugate of the reversed baseline, and the relation $V(u,v,w)=\overline{V(-u,-v,-w)}$ holds. The right-hand side of Eq.\eqref{eq:wstacking} with only positive $w$-value samples then becomes the complex conjugate of the one with only negative $w$-value samples. In this case we can therefore calculate the image for $w<0$ from the image with $w>0$. That allows us to set $w_{\min}$ to the minimum absolute $w$-value, which requires half the number of layers. In any case, the input to the two-dimensional inverse FFT is not generally a Hermitian-symmetric function, and hence the inverse FFT is always performed as a complex-to-complex transform.
